---
title: "visual-assignment"
description: |
  A short description of the post.
author:
  - name: Nikitha Banda
    url: https://www.linkedin.com/in/banda-nikitha
date: 07-10-2021
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE,message=FALSE)
```

## 1.0 Overview

## 2.0 Literature Review of Past Visualization on the same Dataset

## 3.0

## 4.0 Data Processing
As part of the data processing, we first start of by installing the required packages if they are not already installed and calling the libraries. The belo chunk of code will handle all the necessary packages required without one needing to install manually. The required packages will only have to be mentione dthe the 'packages' list.

```{r}
packages = c('readxl','tidyverse','DT')
for(p in packages){
  if(!require(p, character.only = T)){
  install.packages(p)
  }
  library(p, character.only = T)
}
```

### Importing Provided Data

File Name | About
------------- | -------------
EmployeeRecords.xlsx | Cell 2
email headers.csv | Cell 4

```{r}
employee_data <- read_excel("data/EmployeeRecords.xlsx")
#employee_data
email_data <- read_csv("data/email headers.csv")
#email_data
#head(employee_data)
glimpse(email_data)
```

### Processing Email Data

From the dataframes above, it is visible that the data is raw and therefor there is a need to clean it so as to be used for analysis purpose.
Cleaning of email data can be done by performing the below steps :

1. Cleaning email_data
  + 
  ```{r}
  
  ```



## 5.0 ##Response to question ##

## 6.0 Storyboard for R-Shiny

